\section{Discussion}
%Rooted without rebooting
%Unallocated data, and partially overwritten
%Limitations
%Full access to the phone
%Phone memory size
%Timeframe
%1GB memory, 800MB dump
%Writeblock
%Kingroot - what does it do?
%Forensic process
To perform the memory dump, a preliminary research was initiated to discover tools compatible with the smartphone's software; where the criteria were: easy to perform, and minimal alteration of memory. Two different tools were encountered, namely Odin and KingRoot. Both ensure that the phone is rooted, which enable memory dump functionality.
It was unfortunately discovered that Odin was not up to the task, it required: an application to be installed on a computer, connect to it with USB, and a reboot of the phone was required. Because it requires a reboot, any memory content is gone. On the other hand, KingRoot granted root access without rebooting and is therefore preferred. However, it is not recommended to use KingRoot in a real forensics case, due to the fact that the application alters the memory in a unpredictable manner. %TODO: Unpredicatably?
 Reason being that the application is proprietary technology, thus problematic to review the implementation. Consequently, if this research was to be done in a more forensics setting, different methods or tools should be considered. 
\subsection{Limitations}
One of the limitations of this research study was the time frame. Since there was limited time for testing we were unable to verify if the data was stored in the memory for a longer period than tested. The result from the Snapchat application demonstrated that data in the memory will be overwritten over time. On the other hand that would create the possibility to extract other important data. \\\\
 The phone we used did not have a SIM, and for testing purposes the phone did not have any security for unlocking the phone. The logic behind the lack of security was that the project did not focus on security measures, but rather the data in the phone's memory hence given the full access over the phone. \\\\
The phone used for testing had 1GB memory, however, we were able to extract only 800 MB of it. The explanation for the lack of memory could potentially be that there are no mapping directly between the virtual memory and the physical memory. As a result we was unable to access or retrieve this information. While searching through the dumped data no operation system searches was done. However a real forensics case would have done a more thorough search. As a result they would have found more interesting data than we accomplished. \\\\
Throughout dumping of the data we did not use any type of write blocker. As a result there could be data from our dumping that are compromised from connecting the mobile phone to an external device such as the computer used for extraction. For this reason there are a possibility that the RAM memory could have been overwritten or tampered with. \\\\
Another limitation of this research was the test data. There was no real data tested under the forensic phase. This means that we were unable to check for contacts, phone calls and finance information due to the possibility of compromising any of our personal data. Most of the data used in the research was created beforehand for the sole purpose of being easily searched for. 
\subsection{Unallocated, and partially overwritten data}
When preparing the applications for memory collection by plating the prepared strings, several applications were prepared at once, which could have lead to the later data overwriting earlier data. The garbage collector freed some of the memory for reallocation and as more applications were opened the memory was allocated for reuse.

The result was partly overwritten images the was nearly unidentifiable after the data extraction. Reason for this is that the GC focuses mainly on size limits and collision detection when writing new memory. Consequently, if we had a phone with more memory, we could probably have dumped a bigger amount of data.
\subsection{Forensic Process}
The forensic phase did not follow best-practice. For instance there was not any write blockers used which would have made our data integrity trustable. During this process there was no specialized tool used other than the AMExtractor. Therefore the information found and analysed is based on the specific and generic searches that was done by the group. With the use of a forensic specialized tool would have given us the opportunity to find more data of relevance. At the end of the forensic process we can not confirm that the phone used under the forensic process was not tampered with. It is unlikely that the phone had been tampered with, but not provable.