\documentclass[10pt]{sig-alternate-05-2015}
%\usepackage{pdfpages}
%\usepackage{flushend}
\usepackage{lipsum}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{hyperref} 
\usepackage{hypcap}
\usepackage{array}
\usepackage{float}
\usepackage{listingsutf8}
\usepackage{placeins}

\begin{document}
\title{Online Communication Traces in Android Memory}

\numberofauthors{8}
\author{
J{\o}rgen Ellingsen, Espen Kjellstadli Lund, Ingrid Johanne Kjesbu Larsen, Jan Petter Berg Nilsen,\\
Emil Volckmar Ry, Anders Sefjord Torbj{\o}rnsen, Magnus Omland Torgersen, Torstein Ryland Grotle
\\\{jorgeell, espenklu, ingridjl, jpnilsen, emivr, andetorb, magnuoto, torsterg\}@stud.ntnu.no
}

\maketitle
\begin{abstract}
All data are at some point present in memory, but this paper examines what traces of communication survives in memory after the application is closed down. To examine this an Android phone was filled with some of the most used communication applications on the market, and engaged in communications through these. It was then rooted without a reboot and connected to a computer for memory extraction. A market top-selling cleaning tool was also downloaded and ran between data creation and extraction to do as much as a every-day user could practically do to remove communication traces from memory. The experiment had some limitations since we had to root the phone, and we had all the credentials for the phone. Additionally, the phone was not in daily use, and only used during the experiment. The extraction showed traces from all the used applications except Jodel. From Snapchat we found partial images and thumbnail of sent and received images, from Facebook Messenger and Whatsapp we found all communications, and after a map address search we found both the address and the current location of the phone. This showed that a lot of information is accessible in the memory after the application is closed, and this information could persist for a long time depending on the usage and memory requirements of applications run between the generation and the extraction. 
\end{abstract}

\keywords{Android; Memory; Forensics; Practical approach}

\input{introduction}

\input{background}

\input{practicalapproach}

\input{results}

\input{discussion}

\input{conclusion}

\bibliographystyle{vancouver}

\bibliography{b}  

\end{document}
